Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-06-11 paper.qmd
Added descriptions to supplementary table

# Create the table
kable(links_df, 
      format = "latex", 
      booktabs = TRUE, escape = FALSE) |>
  kable_styling(position = "center", 
                full_width = FALSE, 
                font_size = 12) |>
  row_spec(0, bold = TRUE) |>
  column_spec(1:3, width = c("3cm", "5cm", "7cm"))
```

>>>>

# Create the table
kable(links_df, 
      format = "latex", 
      booktabs = TRUE, escape = FALSE) |>
  kable_styling(position = "center", 
                full_width = FALSE, 
                font_size = 12) |>
  row_spec(0, bold = TRUE) |>
  column_spec(1:3, width = c("1cm", "5cm", "9cm"))
```
